Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Removed it again.
Fixed up references.

Its main limitation is that we have not defined a \emph{commutative} comonoid  for any non-empty set $A$ (evidently, $\delta$ is not invariant under postcomposition with the symmetry isomorphism of the tensor). Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is fixed. (This is precisely the situation in SCI, where the typing system allows sharing  across sequential composition, but not between functions and their arguments.) In order to model sharing of state without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a \emph{cofree commutative comonoid}, proposed as the basis of a model of linear logic by Lafont \cite{Laf}.  The category of sets and relations  does not allow this (the cofree commutative comonoid on an object $A$ in $\Rel$ is given by the set of finite multisets of $A$, which is not a final coalgebra). Hence, we turn to the richer structures of game semantics.

@@

@@

By Lemma \ref{aFormulaForAlpha}, the morphism along the bottom is equal to $\alpha_A$ and therefore $g$ is the anamorphism for the morphism along the top; i.e., $g=f^\dag$.

\section{Notes on the construction of transfinite games}

We expand briefly on the construction of transfinite games.

Fix an additively indecomposable ordinal $\alpha=\omega^\beta$.

\end{document}

>>>>

Its main limitation is that we have not defined a \emph{commutative} comonoid  for any non-empty set $A$ (evidently, $\delta$ is not invariant under postcomposition with the symmetry isomorphism of the tensor). Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is fixed. (This is precisely the situation in SCI, where the typing system allows sharing  across sequential composition, but not between functions and their arguments.) In order to model sharing of state without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a \emph{cofree commutative comonoid}, proposed as the basis of a model of linear logic by Lafont \cite{LafontCofCommCom}.  The category of sets and relations  does not allow this (the cofree commutative comonoid on an object $A$ in $\Rel$ is given by the set of finite multisets of $A$, which is not a final coalgebra). Hence, we turn to the richer structures of game semantics.

@@

In particular, $\oc A$ is the final coalgebra for $A\sequoid\blank$.  But, as we showed above, it is not the cofree commutative coalgebra over $A$.

@@

By Lemma \ref{aFormulaForAlpha}, the morphism along the bottom is equal to $\alpha_A$ and therefore $g$ is the anamorphism for the morphism along the top; i.e., $g=f^\dag$.  
\end{document}
